\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-23 chapters/supplementary.tex
Add Elke comments; squeeze for 1st submission

\section{Supplementary Material}

@@

\subsection{Neuron segmentation and compared methods}\label{sec:cremi_details}
\paragraph{Training details} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data. Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
We use L2 loss and Adam optimizer to train the network. % \TODO{Field of view?}

@@

\begin{table}[t]
\centering
    \footnotesize
% \begin{minipage}[T]{0.85\textwidth}
%     \centering
        \begin{tabular}{l|c|c|c|c|c}
          \algname{} linkage & \makecell{Cremi-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
          % Pipeline & method & \textsc{No} & \textsc{Yes} \\

% Average & 0.226 & 0.936 & 0.315 & 0.494 & 
% Sum + CLC & 0.282 & 0.906 & 0.358 & 0.510 & 
% Abs Max & 0.322 & 0.897 & 0.286 & 0.735 & 
% Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 
% Sum & 0.334 & 0.872 & 0.461 & 0.444 & 
% Average + CLC & 0.563 & 0.772 & 0.259 & 1.142 & 
% Min & 2.522 & 0.030 & 0.197 & 6.365 & 
% Min + CLC & 2.522 & 0.030 & 0.197 & 6.365 & 
% Max & 2.626 & 0.028 & 7.069 & 0.026 & 
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0$.}
    \label{tab:extended_results_cremi}
\end{table}
% \hfill
% \begin{minipage}[T]{0.6\textwidth}
% \centering
%         \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
%     \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). \TODO{Overlay raw-data}
%     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
%     %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
%     }
%     \label{fig:noisy_affs}
% \end{minipage}
% \end{figure}

\subsection{Experiments on neuron segmentation adding noise to CNN predictions} \label{sec:appendix_noise_gen}
Additionally to the comparison on the full training dataset, we performed additional experiments on a crop of the dataset\footnote{We chose a challenging part of CREMI training sample B}, where we perturbed the predictions of the CNN with noise and we introduced additional artifacts like missing or fictitious boundary evidences.
% Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a part of the neuron segmentation CREMI dataset. We now present a way of modifying the CNN output to introduce additional artifacts like a missing or false boundary evidence.

@@

The experiments summarized in Fig. \ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria. For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
% one of the dimensions has a lower resolution,   such that three dimensions represent the spatial ones a
% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
% % Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
% % \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
%  % &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
\begin{figure}[t]
\centering
\begin{minipage}[T]{0.6\textwidth}
\centering
        \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the under-clustering biased version $\tilde{F}_{+}$ and c) the over-clustering biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}) \TODO{raw overlay}. 
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
\end{minipage}\hfill
\begin{minipage}[T]{0.35\textwidth}
    \centering
    \footnotesize
        \begin{tabular}{l|c|c}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          % Pipeline & method & \textsc{No} & \textsc{Yes} \\ 
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints}
    \label{tab:extended_results_cityscapes_val}
\end{minipage}
\end{figure}

>>>>

\section{Supplementary material}

@@

\subsection{Neuron segmentation and compared methods}\label{sec:cremi_details}
\paragraph{Training details} The data from the CREMI challenge is highly anisotropic and contains artifacts like missing sections, staining precipitations and support film folds. 
To alleviate difficulties stemming from misalignment, we use a version of the data that was elastically realigned by the challenge organizers with the method of \cite{saalfeld2012elastic}.
We train a 3D U-Net \cite{ronneberger2015u, cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. In addition to the standard data augmentation techniques of random rotations, random flips and  elastic deformations, we simulate data artifacts.
In more detail, we randomly zero-out slices, decrease the contrast of slices, simulate tears, introduce alignment jitter and paste artifacts extracted from the training data. Both \cite{funke2018large} and \cite{lee2017superhuman} have shown
that these kinds of augmentations can help to alleviate issues caused by EM-imaging artifacts.
We use L2 loss and Adam optimizer to train the network. The model was trained on all the three samples with available ground truth labels.

@@

\begin{table}[t]
\centering
    \footnotesize
% \begin{minipage}[T]{0.85\textwidth}
%     \centering
        \begin{tabular}{l|c|c|c|c|c}
          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
          % Pipeline & method & \textsc{No} & \textsc{Yes} \\

% Average & 0.226 & 0.936 & 0.315 & 0.494 & 
% Sum + CLC & 0.282 & 0.906 & 0.358 & 0.510 & 
% Abs Max & 0.322 & 0.897 & 0.286 & 0.735 & 
% Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 
% Sum & 0.334 & 0.872 & 0.461 & 0.444 & 
% Average + CLC & 0.563 & 0.772 & 0.259 & 1.142 & 
% Min & 2.522 & 0.030 & 0.197 & 6.365 & 
% Min + CLC & 2.522 & 0.030 & 0.197 & 6.365 & 
% Max & 2.626 & 0.028 & 7.069 & 0.026 & 
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
    CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0$. We used a machine with CPU Intel(R) Xeon(R) X5650  @ 2.67GHz for our comparison experiments.}
    \label{tab:extended_results_cremi}
\end{table}
% \hfill
% \begin{minipage}[T]{0.6\textwidth}
% \centering
%         \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
%     \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). \TODO{Overlay raw-data}
%     %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
%     %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
%     }
%     \label{fig:noisy_affs}
% \end{minipage}
% \end{figure}

\subsection{Experiments on neuron segmentation adding noise to CNN predictions} \label{sec:appendix_noise_gen}
Additionally to the comparison on the full training dataset, we performed additional experiments on a crop of the more challenging CREMI training sample B, where we perturbed the predictions of the CNN with noise and we introduced additional artifacts like missing or fictitious boundary evidences.
% Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}a} shows an example of uncertain CNN predictions on a part of the neuron segmentation CREMI dataset. We now present a way of modifying the CNN output to introduce additional artifacts like a missing or false boundary evidence.

@@

The experiments summarized in Fig. \ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria. For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
% one of the dimensions has a lower resolution,   such that three dimensions represent the spatial ones a
% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
% % Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
% % \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
%  % &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
\begin{figure}[t]
\centering
\begin{minipage}[T]{0.6\textwidth}
\centering
        \includegraphics[width=0.88\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}
    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the under-clustering biased version $\tilde{F}_{+}$ and c) the over-clustering biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). 
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
\end{minipage}\hfill
\begin{minipage}[T]{0.35\textwidth}
    \centering
    \footnotesize
        \begin{tabular}{l|c|c}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          % Pipeline & method & \textsc{No} & \textsc{Yes} \\ 
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints}
    \label{tab:extended_results_cityscapes_val}
\end{minipage}
\end{figure}
